### 2023-09-30 manuscript.tex
final touch [ci skip]
This build is based on
https://github.com/MMV-Lab/im2im-paper/commit/ea8d01d4ecd397ce1a10f438734ee13bcba943e9.

This commit was created by the following CI build and job:
https://github.com/MMV-Lab/im2im-paper/commit/ea8d01d4ecd397ce1a10f438734ee13bcba943e9/checks
https://github.com/MMV-Lab/im2im-paper/actions/runs/6363677472

This manuscript
(\href{https://MMV-Lab.github.io/im2im-paper/v/46c1a7b20f669efe684592c05b2b9fc37fb62af4/}{permalink})
was automatically generated
from \href{https://github.com/MMV-Lab/im2im-paper/tree/46c1a7b20f669efe684592c05b2b9fc37fb62af4}{MMV-Lab/im2im-paper@46c1a7b}
on September 30, 2023.

@@

\hypertarget{keywords}{%
\subsection{Keywords}\label{keywords}}

Deep learning, biomedical image analysis, image-to-image transformation, open-source

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}@{}}
\caption{Overview of the used frameworks for the demonstrated tasks. \label{tbl:framework_overview}}\label{tbl:framework_overview}\tabularnewline
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
Taskt
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Dim
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Framework
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Backbone
\end{minipage} \\
\midrule()
\endfirsthead
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
Taskt
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Dim
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Framework
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Backbone
\end{minipage} \\
\midrule()
\endhead
Labelfree & 2D/3D & FCN, Pix2pix, cyleGAN & fnet, UNet, AttentionUnet, SwinUNETR, \ldots{} \\
Semantic segmentation & 2D/3D & FCN, cycleGAN & AttentionUnet, DynUnet, UNet3D \\
Instance segmentation & 2D/3D & EmbedSeg & BranchedERFNet\_2d, UNet3D \\
Synthetic & 2D/3D & Pix2pix & AttentionUnet, fnet \\
Denoising & 3D & FCN & UNet \\
Modality transformation & 3D & FCN & UNet3D \\
Staining transformation & 2D & Pix2pix & predefined\_unet \\
\bottomrule()
\end{longtable}

>>>>

This manuscript
(\href{https://MMV-Lab.github.io/im2im-paper/v/ea8d01d4ecd397ce1a10f438734ee13bcba943e9/}{permalink})
was automatically generated
from \href{https://github.com/MMV-Lab/im2im-paper/tree/ea8d01d4ecd397ce1a10f438734ee13bcba943e9}{MMV-Lab/im2im-paper@ea8d01d}
on September 30, 2023.

@@

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}@{}}
\caption{Overview of the used frameworks for the demonstrated tasks. \label{tbl:framework_overview}}\label{tbl:framework_overview}\tabularnewline
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
Task
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Dim
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Framework
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Backbone
\end{minipage} \\
\midrule()
\endfirsthead
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
Task
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Dim
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Framework
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Backbone
\end{minipage} \\
\midrule()
\endhead
Labelfree & 2D/3D & FCN, Pix2pix, cyleGAN & fnet, UNet, AttentionUnet, SwinUNETR, \ldots{} \\
Semantic segmentation & 2D/3D & FCN, cycleGAN & AttentionUnet, DynUnet, UNet3D \\
Instance segmentation & 2D/3D & EmbedSeg & BranchedERFNet\_2d, UNet3D \\
Synthetic & 2D/3D & Pix2pix & AttentionUnet, fnet \\
Denoising & 3D & FCN & UNet \\
Modality transformation & 3D & FCN & UNet3D \\
Staining transformation & 2D & Pix2pix & predefined\_unet \\
\bottomrule()
\end{longtable}
